Storm surges in the Strait of Georgia simulated with a regional model

### 2015-05-04 AO_guides/manuscriptAO.tex
added peak table

\usepackage[natbibapa]{apacite}% Citation support using apacite.sty. Commands using natbib.sty MUST be deactivated first!
\usepackage{color}
\usepackage{hyperref}

@@

\begin{table}[h]
\centering 
\tbl{Evaluation of model performance for all hindcasts presented. Mean absolute error ($\bar{e}$), observed mean (subscript o), modelled mean (subscript m), $\gamma^2$, and the Willmott skill score ($WS$) are provided for water level predictions ($\eta$) and residuals ($\delta$). Statistics are calculated over the time period displayed in each simulation's corresponding figure (three or four days). For the Nov 2006 case, the statistics were calculated over a three day period. The average values were calculated over all of the hindcasts, excluding the Dec 2012 HRDPS simulation. } 
{\begin{tabular}{|l |c c c c c | c c c c c|} 
\hline 
& \multicolumn{5}{|c|}{Water Level ($\eta$)}        & \multicolumn{5}{|c|}{Residual ($\delta$)} \\ 
\hline 
Location       & $\bar{e}$ (cm) & $\bar{\eta_{o}}$ (m) & $\bar{\eta_{m}}$ (m) & $\gamma^2$ & $WS$   & $\bar{e}$ (cm) & $\bar{\delta_{o}}$ (m) & $\bar{\delta_{m}}$ (m) & $\gamma^2$ & $WS$ \\
\hline 
Feb 2006& & & & & & & & & &\\ 
Point Atkinson & 11.6& 3.458& 3.558& 0.012& 0.994& 5.5& 0.318& 0.33& 0.058& 0.985\\
Victoria       & 8.2& 2.182& 2.205& 0.035& 0.99& 5.3& 0.276& 0.298& 0.075& 0.979\\
Patricia Bay   & 10.4& 2.601& 2.678& 0.025& 0.99& 5.5& 0.275& 0.298& 0.066& 0.981\\
Campbell River & 12.2& 3.202& 3.235& 0.034& 0.991& 7.0& 0.27& 0.317& 0.066& 0.973\\
\hline
Nov 2006& & & & & & & & & & \\
Point Atkinson & 10.2& 3.422& 3.499& 0.026& 0.99& 6.7& 0.32& 0.305& 0.128& 0.96\\
Victoria       & 7.8& 2.158& 2.182& 0.065& 0.982& 4.7& 0.246& 0.26& 0.134& 0.961\\
Patricia Bay   & 9.4& 2.565& 2.634& 0.043& 0.983& 5.9& 0.258& 0.261& 0.152& 0.953\\
Campbell River & 9.9& 3.201& 3.243& 0.032& 0.991& 6.3& 0.29& 0.293& 0.153& 0.951\\
\hline
Dec 2006& & & & & & & & & & \\
Point Atkinson & 12.9& 3.452& 3.531& 0.028& 0.99& 10.0& 0.336& 0.33& 0.272& 0.895\\
Victoria       & 8.1& 2.229& 2.226& 0.046& 0.988& 7.2& 0.306& 0.3& 0.227& 0.916\\
Patricia Bay   & 10.2& 2.628& 2.674& 0.035& 0.989& 8.8& 0.308& 0.293& 0.255& 0.896\\
Campbell River & 11.3& 3.234& 3.265& 0.034& 0.991& 8.2& 0.311& 0.304& 0.235& 0.912\\
\hline
Nov 2009& & & & & & & & & & \\
Point Atkinson & 14.5& 3.426& 3.55& 0.01& 0.995& 8.3& 0.344& 0.397& 0.204& 0.897\\
Victoria       & 10.9& 2.249& 2.24& 0.029& 0.992& 4.4& 0.365& 0.361& 0.201& 0.933\\
Patricia Bay   & 12.0& 2.589& 2.685& 0.021& 0.991& 7.4& 0.307& 0.356& 0.216& 0.894\\
Campbell River & 11.6& 3.219& 3.247& 0.016& 0.996& 6.9& 0.341& 0.38& 0.188& 0.915\\
\hline
Dec 2012-CGRF& & & & & & & & & & \\
Point Atkinson & 11.0& 3.362& 3.432& 0.007& 0.997& 5.7& 0.274& 0.273& 0.219& 0.929\\
Victoria       & 12.9& 2.146& 2.111& 0.036& 0.99& 4.7& 0.282& 0.256& 0.175& 0.934\\
Patricia Bay   & 12.8& 2.551& 2.571& 0.024& 0.993& 5.2& 0.275& 0.255& 0.185& 0.934\\
Campbell River & 12.1& 3.064& 3.106& 0.013& 0.996& 8.4& 0.188& 0.263& 0.216& 0.849\\
\hline
Dec 2012-HRDPS& & &  &  &  &  &  &  &  &  \\
Point Atkinson &  10.5&  3.362&  3.42&  0.007&  0.998&  6.2&  0.274&  0.26&  0.231&  0.921\\
Victoria       &  12.6&  2.146&  2.113&  0.035&  0.99&  4.6&  0.282&  0.258&  0.171&  0.937\\
Patricia Bay   &  12.6& 2.551& 2.575& 0.024& 0.993& 5.0& 0.275& 0.26& 0.175& 0.94\\
Campbell River & 12.1& 3.064& 3.104& 0.014& 0.996& 8.1& 0.188& 0.26& 0.218& 0.854\\
\hline
\hline
Averages& & & & & & & & & & \\
Point Atkinson & 11.6&	3.401&	3.483&	0.013&	0.995&	6.7&	0.302&	0.307	&0.192	&0.932\\
Victoria       &10.8&	2.175	&2.162	&0.04	&0.989	&5.1	&0.29	&0.28&	0.167&	0.94\\
Patricia Bay   &11.6&	2.573&	2.619&	0.028&	0.991&	6.0&	0.281&	0.279&	0.179&	0.932\\
Campbell River & 11.6&	3.139&	3.177&	0.021&	0.994&	7.8&	0.246&	0.293&	0.188&	0.893\\
\hline
\end{tabular}}
\label{tab:statistics}
\end{table} 
%anything else to include? statistics calculated in Feb 2006 -paper production.ipynb and saved in statistics_feb2006.CV 
%I also have standard deviations, correlations, ...

>>>>

\usepackage[natbibapa]{apacite}% Citation support using apacite.sty. Commands using natbib.sty MUST be deactivated first!
\usepackage{color}
\usepackage{nohyperref}
\usepackage{url}

@@

\begin{table}[h]
\centering 
\tbl{Evaluation of model performance for all hindcasts presented. Mean absolute error ($\bar{e}$), observed mean (subscript o), modelled mean (subscript m), $\gamma^2$, and the Willmott skill score ($WS$) are provided for water level predictions ($\eta$) and residuals ($\delta$). Statistics are calculated over the time period displayed in each simulation's corresponding figure (three or four days). For the Nov 2006 case, the statistics were calculated over a three day period. The average values were calculated over all of the hindcasts, excluding the Dec 2012 HRDPS simulation. } 
{\begin{tabular}{|l |c c c c c | c c c c c|} 
\hline 
& \multicolumn{5}{|c|}{Water Level ($\eta$)}        & \multicolumn{5}{|c|}{Residual ($\delta$)} \\ 
\hline 
Location       & $\bar{e}$ (cm) & $\bar{\eta_{o}}$ (m) & $\bar{\eta_{m}}$ (m) & $\gamma^2$ & $WS$   & $\bar{e}$ (cm) & $\bar{\delta_{o}}$ (m) & $\bar{\delta_{m}}$ (m) & $\gamma^2$ & $WS$ \\
\hline 
Feb 2006& & & & & & & & & &\\ 
Point Atkinson & 11.6& 3.458& 3.558& 0.012& 0.994& 5.5& 0.318& 0.33& 0.058& 0.985\\
Victoria       & 8.2& 2.182& 2.205& 0.035& 0.99& 5.3& 0.276& 0.298& 0.075& 0.979\\
Patricia Bay   & 10.4& 2.601& 2.678& 0.025& 0.99& 5.5& 0.275& 0.298& 0.066& 0.981\\
Campbell River & 12.2& 3.202& 3.235& 0.034& 0.991& 7.0& 0.27& 0.317& 0.066& 0.973\\
\hline
Nov 2006& & & & & & & & & & \\
Point Atkinson & 10.2& 3.422& 3.499& 0.026& 0.99& 6.7& 0.32& 0.305& 0.128& 0.96\\
Victoria       & 7.8& 2.158& 2.182& 0.065& 0.982& 4.7& 0.246& 0.26& 0.134& 0.961\\
Patricia Bay   & 9.4& 2.565& 2.634& 0.043& 0.983& 5.9& 0.258& 0.261& 0.152& 0.953\\
Campbell River & 9.9& 3.201& 3.243& 0.032& 0.991& 6.3& 0.29& 0.293& 0.153& 0.951\\
\hline
Dec 2006& & & & & & & & & & \\
Point Atkinson & 12.9& 3.452& 3.531& 0.028& 0.99& 10.0& 0.336& 0.33& 0.272& 0.895\\
Victoria       & 8.1& 2.229& 2.226& 0.046& 0.988& 7.2& 0.306& 0.3& 0.227& 0.916\\
Patricia Bay   & 10.2& 2.628& 2.674& 0.035& 0.989& 8.8& 0.308& 0.293& 0.255& 0.896\\
Campbell River & 11.3& 3.234& 3.265& 0.034& 0.991& 8.2& 0.311& 0.304& 0.235& 0.912\\
\hline
Nov 2009& & & & & & & & & & \\
Point Atkinson & 14.5& 3.426& 3.55& 0.01& 0.995& 8.3& 0.344& 0.397& 0.204& 0.897\\
Victoria       & 10.9& 2.249& 2.24& 0.029& 0.992& 4.4& 0.365& 0.361& 0.201& 0.933\\
Patricia Bay   & 12.0& 2.589& 2.685& 0.021& 0.991& 7.4& 0.307& 0.356& 0.216& 0.894\\
Campbell River & 11.6& 3.219& 3.247& 0.016& 0.996& 6.9& 0.341& 0.38& 0.188& 0.915\\
\hline
Dec 2012-CGRF& & & & & & & & & & \\
Point Atkinson & 11.0& 3.362& 3.432& 0.007& 0.997& 5.7& 0.274& 0.273& 0.219& 0.929\\
Victoria       & 12.9& 2.146& 2.111& 0.036& 0.99& 4.7& 0.282& 0.256& 0.175& 0.934\\
Patricia Bay   & 12.8& 2.551& 2.571& 0.024& 0.993& 5.2& 0.275& 0.255& 0.185& 0.934\\
Campbell River & 12.1& 3.064& 3.106& 0.013& 0.996& 8.4& 0.188& 0.263& 0.216& 0.849\\
\hline
Dec 2012-HRDPS& & &  &  &  &  &  &  &  &  \\
Point Atkinson &  10.5&  3.362&  3.42&  0.007&  0.998&  6.2&  0.274&  0.26&  0.231&  0.921\\
Victoria       &  12.6&  2.146&  2.113&  0.035&  0.99&  4.6&  0.282&  0.258&  0.171&  0.937\\
Patricia Bay   &  12.6& 2.551& 2.575& 0.024& 0.993& 5.0& 0.275& 0.26& 0.175& 0.94\\
Campbell River & 12.1& 3.064& 3.104& 0.014& 0.996& 8.1& 0.188& 0.26& 0.218& 0.854\\
\hline
\hline
Averages& & & & & & & & & & \\
Point Atkinson & 11.6&	3.401&	3.483&	0.013&	0.995&	6.7&	0.302&	0.307	&0.192	&0.932\\
Victoria       &10.8&	2.175	&2.162	&0.04	&0.989	&5.1	&0.29	&0.28&	0.167&	0.94\\
Patricia Bay   &11.6&	2.573&	2.619&	0.028&	0.991&	6.0&	0.281&	0.279&	0.179&	0.932\\
Campbell River & 11.6&	3.139&	3.177&	0.021&	0.994&	7.8&	0.246&	0.293&	0.188&	0.893\\
\hline
\end{tabular}}
\label{tab:statistics}
\end{table} 
%anything else to include? statistics calculated in Feb 2006 -paper production.ipynb and saved in statistics_feb2006.CV 
%I also have standard deviations, correlations, ...
\begin{table}[h]
\centering 
\tbl{{\color{red}Summary of maximum water level, maximum surge amplitude and model delay for all simulations. The model time delay is the number of hours between the maximum in the observations and the maximum in the model. A negative number means the model's maximum was later than the observations. Values calucated over the same periods discusses in Table \ref{tab:statistics}. } }
{\begin{tabular}{|l |c c c | c c c|} 
\hline 
& \multicolumn{3}{|c|}{Water Level ($\eta$)}        & \multicolumn{3}{|c|}{Residual ($\delta$)} \\ 
\hline 
Location       & Max obs (m) & Max mod (m) & Delay (hours) &Max obs (m) & Max mod (m) & Delay (hours) \\
\hline
Feb 2006&  &  &  &  &  & \\
Point Atkinson  & 5.460 & 5.588 & 0 & 0.844 & 0.841 & -3\\
Victoria        & 3.440 & 3.415 & -1 & 0.700 & 0.745 & 1\\
Patricia Bay    & 4.250 & 4.179 & -1 & 0.781 & 0.773 & -2\\
Campbell River  & 5.100 & 5.170 & -1 & 0.876 & 0.815 & -5\\
\hline
Nov 2006 &  &  &  &  &  & \\
Point Atkinson  & 5.010 & 5.040 & 0 & 0.880 & 0.725 & 1\\
Victoria        & 2.995 & 2.968 & 1 & 0.664 & 0.563 & 5\\
Patricia Bay    & 3.840 & 3.743 & 0 & 0.709 & 0.607 & 2\\
Campbell River  & 4.750 & 4.739 & 0 & 0.709 & 0.666 & -1\\
\hline
Dec 2006 &  &  &  &  &  & \\
Point Atkinson  & 4.565 & 4.654 & 0 & 0.944 & 0.699 & 0\\
Victoria        & 2.965 & 3.005 & -1 & 0.737 & 0.580 & 1\\
Patricia Bay    & 3.505 & 3.480 & 0 & 0.859 & 0.613 & 1\\
Campbell River  & 4.295 & 4.389 & -1 & 0.823 & 0.626 & 0\\
\hline
Nov 2009 &  &  &  &  &  & \\
Point Atkinson  & 5.150 & 5.272 & 0 & 0.699 & 0.587 & -7\\
Victoria        & 3.195 & 3.144 & -4 & 0.718 & 0.540 & -8\\
Patricia Bay    & 3.985 & 3.902 & 0 & 0.637 & 0.541 & -8\\
Campbell River  & 4.680 & 4.782 & 0 & 0.664 & 0.588 & -1\\
\hline
Dec 2012-CRGF &  &  &  &  &  & \\
Point Atkinson  & 5.345 & 5.416 & 0 & 0.663 & 0.555 & -4\\
Victoria        & 3.145 & 3.117 & 0 & 0.663 & 0.518 & -4\\
Patricia Bay    & 4.115 & 3.975 & 0 & 0.632 & 0.533 & -4\\
Campbell River  & 4.805 & 4.900 & 0 & 0.578 & 0.507 & -6\\
\hline
Dec 2012-HRDPS &  &  &  &  &  & \\
Point Atkinson  & 5.345 & 5.414 & 0 & 0.663 & 0.555 & -4\\
Victoria        & 3.145 & 3.123 & 0 & 0.663 & 0.518 & -4\\
Patricia Bay    & 4.115 & 3.984 & 0 & 0.632 & 0.533 & -4\\
Campbell River  & 4.805 & 4.905 & 0 & 0.578 & 0.511 & -6\\
\hline
\hline
Averages  &  &  &  &  &  & \\
Point Atkinson  & 5.196 & 5.277 & 0  & 0.752 & 0.634 & -3.125\\
Victoria        & 3.147 & 3.125 & -0.625 & 0.684 & 0.563 & -2.125\\
Patricia Bay    & 4.005 & 3.901 & -0.125 & 0.689 & 0.584 & -2.875\\
Campbell River  & 4.756 & 4.835 & -0.250 & 0.673 & 0.590 & -3.875\\ 
\hline 
\end{tabular}}
\label{tab:peak}
\end{table}
